Datasheet for Children's Book Ratings

### 2023-03-25 outputs/paper/paper.qmd
Completed Motivation section of datasheet

-   **For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.**
    -   The dataset was created to address the problem of inconsistency on rating sites and to estimate more reasonable ratings, specifically for children's books by using empirical Bayes estimation.
-   **Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?**
    -   Alex Cookson, while working at the Royal Canadian Mint.
-   **Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.**
    -   No direct funding was received for this project.
-   **Any other comments?**
    -   No.

>>>>

-   **For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.**
    -   The dataset was created to address the issue of inconsistency on rating sites. This problem arises when different rating platforms, such as Rotten Tomatoes or Amazon, have identical ratings but have varying implications, causing an uncertainty in which rating to trust. It was also created to estimate more reasonable ratings, specifically for children's books, by using empirical Bayes estimation.
-   **Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?**
    -   Alex Cookson, while working at the Royal Canadian Mint.
-   **Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.**
    -   No direct funding was received for this project.
-   **Any other comments?**
    -   No.
